---
title: "Day 5 Morning Session"
author: Matteo Torres
format: html
execute: 
  warning: false
editor_options: 
  chunk_output_type: console
---

```{r}
#| message: false
# load packages ----
library(tidyverse)
```

`head()`, `tail()`, and `dim()` on the `dplyr::starwars` data frame:
```{r}
#| include: false
# do some data exploration on the starwars df ----
head(starwars)

tail(starwars)

dim(starwars)
```

- Create a ggplot (scatterplot) of character mass (y-axis) and height (x-axis)
- Update the color of the points so that color changes based on the value of `mass`
```{r}
#| echo: false
ggplot(data= starwars, aes(x= height, y= mass, color= mass))+
  geom_point(color= "green") +
  labs(x= "Height (cm)", y= "Mass (kg)", title= "Starwars Characters")
```

- Create a histogram fo character heights
- Update the fill color (`fill`) to purple and the outside border line (`color`) of each histogram to orange
- Update the axis labels
- Update your code chunk options so that only the code and output graph appear in the rendered doc (no warnings or messages)
```{r}
#| fig-cap: "From short kings/queens to next year's possible NBA draft!"
#| fig-alt: "This is my alt text ig"
ggplot(data= starwars, aes(x= height)) +
  geom_histogram(color= "orange", fill= "purple") +
  labs(x= "Height (cm)", y= "Frequency", title= "Starwars Characters")
```

`df$col_name`

```{r}
sw_height_mean<- round(mean(starwars$height, na.rm= TRUE), digits= 3)
```

The mean height of all starwars characters is `r sw_height_mean`
